Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-04 paper/ms.tex
Make discussion section into subsections, add applicability to Milky Way

To gain further handle on the midplane behavior as a function of azimuth, we
compute the range of midplane values for a given $\Delta \phi$ segment of the
midplane in Figure~\ref{fig:range_deltaphi}. With the observer's azimuth set
to zero, we consider a region extending from $-\Delta \phi/2$ to
$\Delta\phi/2$. We also compute the chord length for the chord extending from
the observer to $\pm \Delta\phi/2$. We repeat this for each of the $50$ bins
in azimuth. Each bin is plotted as a gray line, with the mean value in solid
blue and the $1\,\sigma$ dispersion as the dashed blue lines.

>>>>

\subsection{Applicability to the Milky Way} \label{ssec:is_it_real}
As we briefly discussed in Section~\ref{ssec:cosmozoom}, cosmological zoom-in
simulations of Milky Way-mass galaxies are not perfect representations of the
Milky Way, and do not reproduce every available observation of the Milky Way.
For instance, the velocity dispersion-age relation in m12i, m12f, and m12m is
closer to that of M31 \citep{2018arXiv180610564S}.

In order to assess the applicability of our work to the real Milky Way, we
consider a subset of Table~3 from \citet{2018arXiv180610564S} --- our
Table~\ref{tab:scale_height} shows the stellar scale heights of m12i, m12f,
and m12m and the current best estimates for the Milky Way. One noticeable
feature is that the FIRE galaxies are more ``puffy'' than the Milky Way.
\Gus{Maybe FIRE collaboration has some insight into the mechanism for this?}.
This would seem to suggest that the midplane estimates from
Figure~\ref{fig:midplane} over-estimate the true variation in the Milky Way.

\begin{deluxetable}{ccc}
\tablecaption{Stellar Disk Scale Heights}
\tablehead{\colhead{galaxy} & \colhead{thin disk} & \colhead{thick disk} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{a} & 300 & 900 \\
m12i\tablenotemark{b} & 480 & 2000 \\
m12f\tablenotemark{b} & 440 & 1280 \\
m12m\tablenotemark{b} & 290 & 1030 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}

\tablenotetext{a}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{b}{\citet{2018arXiv180610564S}}

\label{tab:scale_height}
\end{deluxetable}

Another important aspect to consider when comparing the simulated galaxies to
the Milky Way is the environment/merger history. For instance, m12i and m12m
both lack a massive neighbor analogous to the LMC. On the other hand, m12f has
had a recenter merger with \Gus{something}. \Gus{Expand more here - how to
incorporate merger trees?}

\subsection{Solar Neighborhood} \label{ssec:neighborhood}
To gain further handle on the midplane behavior as a function of azimuth, we
compute the range of midplane values for a given $\Delta \phi$ segment of the
midplane in Figure~\ref{fig:range_deltaphi}. With the observer's azimuth set
to zero, we consider a region extending from $-\Delta \phi/2$ to
$\Delta\phi/2$. We also compute the chord length for the chord extending from
the observer to $\pm \Delta\phi/2$. We repeat this for each of the $50$ bins
in azimuth. Each bin is plotted as a gray line, with the mean value in solid
blue and the $1\,\sigma$ dispersion as the dashed blue lines.
